---
title: "Final Project"
author: "Grace Montgomery"
subtitle: MGSC 410 Problem Set Template
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}
library(knitr)

# general rchunk code options

# this sets text to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')


```

## Loading Libraries

```{r}
rm(list = ls())
set.seed(1818)
options(scipen = 9)
```

```{r}
library('magrittr')
library('dplyr')
library('tidyr')
library('tidyverse')
library('ggridges')
library('gganimate')
library('forcats')
library('rsample')
library('glmnet')
library('glmnetUtils')
library('broom')
library('coefplot')
library('cluster')
library('factoextra')
library('NbClust')

```

# More libraries 
```{r}
library("dendextend")

```

Loading datasets

```{r}
app_activity <- read.csv(here::here("cleaned_data", "app_activity.csv"))
raw_data <- read.csv(here::here("cleaned_data", "master_data_forR.csv"), na.strings = "NULL")
```

Data Manipulation
#changed Purchase.Amount.In.USD to a numeric in excel and replaced the $- to 0
```{r}

master_data <- raw_data %>% select(-ï..ID,-Purchase.Amount,-Subscription.Event.Type,
                                   -Subscription.Type,-Purchase.Store,-Subscription.Start.Date,
                                   -Subscription.Expiration,-Demo.User,-Free.Trial.User,
                                   -Free.Trial.Start.Date, -Free.Trial.Expiration,-Auto.Renew,
                                   -User.Type,-Lead.Platform, -Email.Subscriber,-Push.Notifications)

master_data <- master_data %>% mutate(
  Purchase.Amount.in.USD = as.numeric(Purchase.Amount.in.USD),
  Langauge = as.factor(Language),
  isSubscriptionTypeLifetime = as.factor(isSubscriptionTypeLifetime),
  isSubscriptionEventTypeRenewal = as.factor(isSubscriptionEventTypeRenewal),
  isPurchaseStoreWeb = as.factor(isPurchaseStoreWeb),
  Currency = as.factor(Currency),
  isDemoUser = as.factor(isDemoUser),
  isFreeTrialUser = as.factor(isFreeTrialUser),
  isAutoRenew = as.factor(isAutoRenew),
  Country = as.factor(Country),
  isUserTypeConsumer = as.factor(isUserTypeConsumer),
  isLeadPlatformWeb = as.factor(isLeadPlatformWeb),
  isEmailSubscriber = as.factor(isEmailSubscriber),
  isPushNotifications = as.factor(isPushNotifications)
  ) 
# %>% select(-Langauge)
# master_data<- normalize(master_data)

```

#First attempt cluster unsupervised Hierarchical Agglomerative Clustering
Variables: Language, Purchase Amount,Subscription Type, Send count, Open count, Click count, Unique open count, Unique click count

https://www.datacamp.com/community/tutorials/hierarchical-clustering-R
https://uc-r.github.io/hc_clustering

HA cluttering code
```{r}

# HA_clust_df <- raw_data %>% 
#   select(Language, Purchase.Amount.in.USD, Subscription.Type, Send.Count, Open.Count, Click.Count, Unique.Open.Count, Unique.Click.Count) %>% 
#   mutate(
#     Language = as.factor(Language),
#     Subscription.Type = as.factor(Subscription.Type)
#   ) %>% 
#   select(-Language, -Subscription.Type)
# 
# #omit NA's
# HA_clust_df <- na.omit(HA_clust_df)
# # HA_clust_df <- scale(HA_clust_df)

```

```{r}

# summary(raw_data)

# newdata <- 

```


```{r}
# # Dissimilarity Matrix
# d <- dist(HA_clust_df, method = "euclidean")
# # Hierarchical clustering using complete linkage
# hcl <- hclust(d, method = "complete")
# #PLot dendrogram
# plot(hcl, cex = 0.6, hang = -1)

```

```{r}

# HA_clust2 <- master_data %>% 
#   select(Language, Purchase.Amount.in.USD, Subscription.Type, Send.Count, Open.Count, Click.Count, Unique.Open.Count, Unique.Click.Count) 
#   #  %>% 
  # mutate(
  #   Language = as.factor(Language),
  #   Subscription.Type = as.factor(Subscription.Type)
  # ) %>% 
  # select(-Language, -Subscription.Type)

#omit NA's
# HA_clust2 <- na.omit(HA_clust2)
# HA_clust2 <- scale(HA_clust2)

```


```{r}
# # Dissimilarity Matrix
# d2 <- dist(HA_clust2, method = "euclidean")
# # Hierarchical clustering using complete linkage
# hcl2 <- hclust(d2, method = "complete")
# #PLot dendrogram
# plot(hcl2, cex = 0.6, hang = -1)

```
```{r}

ggplot(master_data, aes(
                          # x = Language,
                          x = Purchase.Amount.in.USD)) +
  geom_histogram()

```

```{r}

ggplot(master_data, aes(x = Language))+
  facet_wrap("Country")+
  geom_histogram(stat="count")

```

```{r}

# ggplot(master_data, aes(x = Subscription.Event.Type, y = Purchase.Amount.in.USD))+
#   facet_wrap("Country")+
#   geom_boxplot()

```



#ENet mod
```{r}

enet_mod1 <- cva.glmnet(Purchase.Amount.in.USD ~ .-isPurchaseStore,
                       data = master_data,
                       alpha = seq(0,1, by = 0.05))

plot(enet_mod1)

minlossplot(enet_mod1, 
            cv.type = "min")

```

```{r}

# Use this function to find the best alpha
get_alpha <- function(fit) {
  alpha <- fit$alpha
  error <- sapply(fit$modlist, 
                  function(enet_mod1) {min(enet_mod1$cvm)})
  alpha[which.min(error)]
}

# Get all parameters.
get_model_params <- function(fit) {
  alpha <- fit$alpha
  lambdaMin <- sapply(fit$modlist, `[[`, "lambda.min")
  lambdaSE <- sapply(fit$modlist, `[[`, "lambda.1se")
  error <- sapply(fit$modlist, function(enet_mod1) {min(enet_mod1$cvm)})
  best <- which.min(error)
  data.frame(alpha = alpha[best], lambdaMin = lambdaMin[best],
             lambdaSE = lambdaSE[best], eror = error[best])
}

# extract the best alpha value and model parameters
best_alpha <- get_alpha(enet_mod1)
print(best_alpha)
get_model_params(enet_mod1)

```

#Almost Lasso

```{r}
lasso_mod <- cv.glmnet(Purchase.Amount.in.USD ~ .-isPurchaseStoreWeb,
                       data = master_data,
                       # note alpha = 1 sets Lasso!
                       alpha = 0.95)

# print(lasso_mod$lambda.min)
# print(lasso_mod$lambda.1se)

# plot(lasso_mod)


coefpath(lasso_mod)


```

```{r}

coef(lasso_mod, 
     s = lasso_mod$lambda.min) %>% 
  round(3)
```



#Language
```{r}

enet_mod_lang <- cva.glmnet(Purchase.Amount.in.USD ~ Language,
                       data = master_data,
                       alpha = seq(0,1, by = 0.05))

minlossplot(enet_mod_lang, 
            cv.type = "min")

```

```{r}

# Use this function to find the best alpha
get_alpha <- function(fit) {
  alpha <- fit$alpha
  error <- sapply(fit$modlist, 
                  function(enet_mod_lang) {min(enet_mod_lang$cvm)})
  alpha[which.min(error)]
}

# extract the best alpha value and model parameters
best_alpha <- get_alpha(enet_mod_lang)
print(best_alpha)

```


```{r}
mod_lang <- cv.glmnet(Purchase.Amount.in.USD ~ Language, #ask ben, using the wrong language variable?
                       data = master_data,
                       alpha = 0.05) #Almost Ridge

coefpath(mod_lang)

coef(mod_lang, 
     s = mod_lang$lambda.min) %>% 
  round(3)

```




#Currency
```{r}

enet_mod_currency <- cva.glmnet(Purchase.Amount.in.USD ~ Currency,
                       data = master_data,
                       alpha = seq(0,1, by = 0.05))

minlossplot(enet_mod_currency, 
            cv.type = "min")

```

```{r}

# Use this function to find the best alpha
get_alpha <- function(fit) {
  alpha <- fit$alpha
  error <- sapply(fit$modlist, 
                  function(enet_mod_currency) {min(enet_mod_currency$cvm)})
  alpha[which.min(error)]
}

# extract the best alpha value and model parameters
best_alpha <- get_alpha(enet_mod_currency)
print(best_alpha)

```


```{r}
mod_currency <- cv.glmnet(Purchase.Amount.in.USD ~ Currency,
                       data = master_data,
                       alpha = 0) 

coefpath(mod_currency)

coef(mod_currency, 
     s = mod_lang$lambda.min) %>% 
  round(3)

```

#-Langauge and -Currency
```{r}

enet_mod_subset <- cva.glmnet(Purchase.Amount.in.USD ~. -Language-Currency-Langauge-isPurchaseStoreWeb,
                       data = master_data,
                       alpha = seq(0,1, by = 0.05))

minlossplot(enet_mod_subset, 
            cv.type = "min")

```

```{r}

# Use this function to find the best alpha
get_alpha <- function(fit) {
  alpha <- fit$alpha
  error <- sapply(fit$modlist, 
                  function(enet_mod_subset) {min(enet_mod_subset$cvm)})
  alpha[which.min(error)]
}

# extract the best alpha value and model parameters
best_alpha <- get_alpha(enet_mod_subset)
print(best_alpha)

```


```{r}
mod_subset <- cv.glmnet(Purchase.Amount.in.USD ~ .-Language-Currency-Langauge-isPurchaseStoreWeb,
                       data = master_data,
                       alpha = 0.05) 

coefpath(mod_subset)

coef(mod_subset, 
     s = mod_subset$lambda.min) %>% 
  round(3)

```




