---
title: "Grace Code V2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading Libraries

```{r}
rm(list = ls())
set.seed(1818)
options(scipen = 9)
```

```{r}
library('magrittr')
library('dplyr')
library('tidyr')
library('tidyverse')
library('ggridges')
library('gganimate')
library('forcats')
library('rsample')
library('glmnet')
library('glmnetUtils')
library('broom')
library('coefplot')
library('cluster')
library('factoextra')
library('NbClust')
library("dendextend")

```


Loading datasets

```{r}
app_activity <- read.csv(here::here("cleaned_data", "app_activity.csv"))
raw_data <- read.csv(here::here("cleaned_data", "master_data_forR_noNULL.csv"), na.strings = "NULL") #without nulls
head(raw_data)
```

Data Manipulation
#changed Purchase.Amount.In.USD to a numeric in excel and replaced the $- to 0
```{r}

master_data <- raw_data %>% select(-ï..ID,-Purchase.Amount,-Subscription.Event.Type,
                                   -Subscription.Type,-Purchase.Store,-Subscription.Start.Date,
                                   -Subscription.Expiration,-Demo.User,-Free.Trial.User,
                                   -Free.Trial.Start.Date, -Free.Trial.Expiration,-Auto.Renew,
                                   -User.Type,-Lead.Platform, -Email.Subscriber,-Push.Notifications)

master_data <- master_data %>% mutate(
  Purchase.Amount.in.USD = as.numeric(Purchase.Amount.in.USD),
  isSubscriptionTypeLifetime = as.factor(isSubscriptionTypeLifetime),
  isSubscriptionEventTypeRenewal = as.factor(isSubscriptionEventTypeRenewal),
  isPurchaseStoreWeb = as.factor(isPurchaseStoreWeb),
  Currency = as.factor(Currency),
  isDemoUser = as.factor(isDemoUser),
  isFreeTrialUser = as.factor(isFreeTrialUser),
  isAutoRenew = as.factor(isAutoRenew),
  Country = as.factor(Country),
  isUserTypeConsumer = as.factor(isUserTypeConsumer),
  isLeadPlatformWeb = as.factor(isLeadPlatformWeb),
  isEmailSubscriber = as.factor(isEmailSubscriber),
  isPushNotifications = as.factor(isPushNotifications)
  ) 

master_data$Language <- as.factor(master_data$Language) 
  # subs$Country <- as.factor(subs$Country)
##subs$User.Type <- to_logical(subs$User.T

# %>% select(-Langauge)
# master_data<- normalize(master_data)
head(master_data)
```
```{r}
summary(master_data)

```

#ENet mod
```{r}

enet_mod1 <- cva.glmnet(Purchase.Amount.in.USD ~ .-isPurchaseStore,
                       data = master_data,
                       alpha = seq(0,1, by = 0.05))

plot(enet_mod1)

minlossplot(enet_mod1, 
            cv.type = "min")

```

```{r}

# Use this function to find the best alpha
get_alpha <- function(fit) {
  alpha <- fit$alpha
  error <- sapply(fit$modlist, 
                  function(enet_mod1) {min(enet_mod1$cvm)})
  alpha[which.min(error)]
}

# Get all parameters.
get_model_params <- function(fit) {
  alpha <- fit$alpha
  lambdaMin <- sapply(fit$modlist, `[[`, "lambda.min")
  lambdaSE <- sapply(fit$modlist, `[[`, "lambda.1se")
  error <- sapply(fit$modlist, function(enet_mod1) {min(enet_mod1$cvm)})
  best <- which.min(error)
  data.frame(alpha = alpha[best], lambdaMin = lambdaMin[best],
             lambdaSE = lambdaSE[best], eror = error[best])
}

# extract the best alpha value and model parameters
best_alpha <- get_alpha(enet_mod1)
print(best_alpha)
get_model_params(enet_mod1)

```

#Almost Lasso

```{r}
general_mod <- cv.glmnet(Purchase.Amount.in.USD ~ .-isPurchaseStoreWeb,
                       data = master_data,
                       # note alpha = 1 sets Lasso!
                       alpha = 0.85)
# plot(lasso_mod)
coefpath(general_mod)

```

```{r}

coef(general_mod, 
     s = general_mod$lambda.min) %>%
  round(3)
```


```{r}
coef(general_mod, 
     s = general_mod$lambda.1se) %>%
  round(3)

```

```{r}

write.csv(Your DataFrame,"Path where you'd like to export the DataFrame\\File Name.csv", row.names = FALSE)


```


```{r}

write.csv(Your DataFrame,"Path where you'd like to export the DataFrame\\File Name.csv", row.names = FALSE)


```


#Logistic Regression
Logistic regression model
People who renew subscriptions -> more likely to buy additional products/services
Variables: Language, Demo User, Free Trial User, Email Subscription, Country, #Purchase Store, 
App Session 
Platform, Lead Platform

```{r}
library('yardstick')
```

```{r}

train_prop <- 0.8
master_split <- initial_split(master_data, prop = train_prop)

master_train <- training(master_split)
master_test <- testing(master_split)

isSubscriptionEventTypeRenewal

```

```{r}
logit_fit1 <- glm(isSubscriptionEventTypeRenewal ~ Language + isDemoUser + isFreeTrialUser + isEmailSubscriber + Country + App.Session...android + App.Session...ios,
                  family = binomial,
                  data = master_train)

# rounding thing for scientific notation 
options(scipen = 9)

#exponentiation
exp(logit_fit1$coefficients)

#confusion matrix
conf_mat(two_class_example, 
         truth = truth, 
         estimate = predicted)
scores <- predict(logit_fit1,
                  newdata = master_train)

results_logit <- data.frame(
  `truth` = as.factor(master_train$isSubscriptionEventTypeRenewal),
  `Class1` =  scores,
  `Class2` = 1 - scores,
  `predicted` = as.factor(ifelse(scores > 0.4,
                                 "Yes","No"))
)


```

```{r}
cm <- conf_mat(results_logit, 
               truth = truth,
               estimate = predicted)

print(cm)
autoplot(cm, "heatmap")

```

```{r}
# ROC Plots
library('plotROC')

p <- ggplot(results_logit, 
            aes(m = Class1, d = truth)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.99,0.9,0.7,0.5,0.3,0.1,0)) +
  theme_minimal(base_size = 16)
print(p)
calc_auc(p)

roc_auc(results_logit, 
        truth = truth, 
        estimate = predicted)

```















































